The impact of winning the coin toss on the Indian Premier League

### 2021-01-21 inst/T20.Rmd
consistentify T20 dataset

```{r}
library("hyper2",quietly=TRUE)
head(T20_table)
nrow(T20_table)
```

@@

```{r}
attach(lapply(T20_table[, ], as.vector))  # vector access to team1, etc
T20 <- hyper2(pnames=c(levels(T20_table$team1)))
for(i in seq_along(team1)){
   T20[match_winner[i]] %<>% inc
   T20[c(team1[i],team2[i])] %<>% dec

@@

```{r}
dotchart(maxp(T20))
```

@@

```{r}
dotchart(maxp(T20_toss))
```

@@

>>>>

```{r}
library("hyper2",quietly=TRUE)
T20_table <- read.table("T20.txt",header=TRUE)
head(T20_table)
nrow(T20_table)
```

@@

```{r}
attach(lapply(T20_table[, ], as.vector))  # vector access to team1, etc
T20 <- hyper2()
for(i in seq_along(team1)){
   T20[match_winner[i]] %<>% inc
   T20[c(team1[i],team2[i])] %<>% dec

@@

```{r}
T20_maxp <- maxp(T20)
dotchart(T20_maxp)
```

@@

```{r}
T20_maxp_toss <- maxp(T20_toss)
dotchart(T20_maxp_toss)
```

@@

### Package dataset

The following lines create `T20.rda`, residing in the `data/`
directory of the package.

```{r,label=saveT20dataset}
save(T20_table,T20,T20_maxp,T20_toss,file="T20.rda")
```
